Intended Table of Contents Thesis

### 2013-02-08 Chapters/Chapter2.tex
Cleanup. Extented intended contents

A second approach in~\cite{barbivc2004segmenting} uses the probabilistic variant of PCA (PPCA) to model the data set as a Gaussian distribution instead of ignoring the frames which do not fit in the subspace.
Over windows of frames the mean and variance are calculated.
In a forward manner the Mahalanobis distance of a new window of frames is calculated, which represents the likelihood of the new window belonging to the same segment as the original widow.
When the distance decreases, the likelihood increases which happens when the motions in the becomes more homogeneous.
When a peak in the distance is reached, the new window of frames indicates a heterogeneous collection of motions in the window and thus a low likelihood of membership and a indication of a transition.
In order to distinct activities and subactivities (which require a subset of motions is a distinct activity) the algorithm is also processed backward over the data series.

>>>>

A second approach in~\cite{barbivc2004segmenting} uses the probabilistic variant of PCA (PPCA) to model the data set as a Gaussian distribution instead of ignoring the frames which do not fit in the subspace.
Over windows of frames the mean and variance are calculated.
In a forward manner the Mahalanobis distance of a new window of frames is calculated, which represents the likelihood of the new window belonging to the same segment as the original widow.
When the distance decreases, the likelihood increases which happens when the motions in the becomes more homogeneous.
When a peak in the distance is reached, the new window of frames indicates a heterogeneous collection of motions in the window and thus a low likelihood of membership and a indication of a transition.
In order to distinct activities and sub-activities (which require a subset of motions is a distinct activity) the algorithm is also processed backward over the data series.

### 2013-02-08 intended_contents.tex
Added drafts for some diagrams
Removed linebreaks
Cleanup. Extented intended contents

\section{Introduction}
This section introduces the subject, outlines the global goal of the thesis
and explains the problem. The main research-questions are introduced. In the
subsections the main components (global, not as an implementation) are
introduced.

  \subsection{Thesis goal}
  The goal of the thesis will be discussed, e.g. "precise unsupervised on-line human activity recognition". Mention application to show why it is useful.

@@

\section{Concepts}

  \subsection{Temporal pattern recognition}
  This will explain about what patterns are and what kind of patterns need to be recognized (long-term, short-term repetitive, etc)

	\subsection{Signal pre-processing}
  Describe how data is collected and processed. Include feature extraction, like PCA, FFT. Mention only shortly with meaning, no further explanation.

	\subsection{Temporal Segmentation}
  What is segmentation, the purpose and what kind of methods are there. E.g. model-based, statistics-based. Diagram with types. Supervised / unsupervised. HMMs, Statistical, Bayesian. K-means, SOM

  \subsection{Temporal clustering}
  When is segmenting clustering? Explain difference, mention techniques (diagrams), Dynamic Time Warping, k-means (and variations), SOM, SVM, Naive Bayes, Neural Networks.

\section{Problem statement}
This section proposes a setup to improve (or: answer) the research-questions. It will discuss techniques used in other projects and how implemented here. In the subsections each used technique is further explained. (Only explained when really used)

@@

\section{Implementation}
This section will discuss implementation details. Hardware platform (if any), software used. Complexity, precision of metrics etc.

\section{Experiments, results}
This section will outline the precise experiments and gives the results of these.

\section{Discussion}
This section will discuss the results of the previous section. It will relate the results to previous work.

\section{Conclusion}
Conclusion (answer research question), summary of results, feature work.

>>>>

\section{Introduction}
\label{sec:Introduction}
This section introduces the subject, outlines the global goal of the thesis and explains the problem.
The main research-questions are introduced.
In the subsections the main components (global, not as an implementation) are introduced.
Outline of the thesis is presented.
Chapter~\ref{sec:Concepts} introduces the big parts of the puzzle.
Chapter~\ref{sec:Setup} gives details about the algorithms used.
Chapter~\ref{sec:Implementation} will give the implementation details.
Chapter~\ref{sec:Experiments} will show how data is gathered and shows the data.
Chapter~\ref{sec:Discussion} will discuss and relate the results
Chapter~\ref{sec:Conclusion} will conclude and give final remarks.

  \subsection{Thesis goal}
  The goal of the thesis will be discussed, e.g. "precise unsupervised on-line human activity recognition".
  Mention application to show why it is useful, such as medical and other health (losing weight, fitness) problems.
  The main research questions will be formulated here.

@@

\section{Concepts}
\label{sec:Concepts}
This chapter will introduce the abstract concepts which will be used.
There will be some formulas, but minimal implementations.
The focus is on the meaning of the terms and what they do and how they do it.
Real implementations will be discussed in chapter~\ref{sec:Setup}.

  \subsection{Temporal pattern recognition}
  This will explain about what patterns are and what kind of patterns need to be recognized (long-term, short-term repetitive, etc).
  This is not specific about segmentation of clustering, but more as the ultimate goal.

	\subsection{Signal pre-processing}
  Describe how data is collected and processed, the form of the data (continuous to discrete, amplitude, energy, frequencies, etc).
  Include feature extraction, like PCA, FFT, energy, mean, but discuss it further in subsection.
  Only the concepts will be explained and the scheme of the computations (or simply formulas), no precise implementations.
  Mention only shortly with meaning, no further explanation.

    \subsubsection{Signal fusion}
    What, why and how.

    \subsubsection{Signal smoothing}
    What, why and how.

    \subsubsection{Feature extraction}
    What, why and how.

	\subsection{Temporal Segmentation}
  What is segmentation, the purpose and what kind of methods are there.
  Disctinction with clustering.
  E.g. model-based, statistics-based.
  Diagram with types.
  Supervised / unsupervised.

    \subsubsection{Methods}
    Describe methods, such as HMMs, Statistical, Bayesian. K-means, SOM

  \subsection{Temporal clustering}
  When is segmenting clustering?
  Explain difference of point of view/mechanism, mention techniques (diagrams).
  This is the unsupervised part.

    \subsubsection{Methods}
    Explain difference in techniques and give schematic overview of inner workings.
    Dynamic Time Warping, k-means (and variations), SOM, SVM, Naive Bayes, Neural Networks.

  \subsection{Matching}
  Not really sure about this section yet.
  It would be about matching new on-line gathered data with already learned patterns.
  But maybe it is more of a on-line combination of segmentation and clustering.

\section{Algorithms setup}
\label{sec:Setup}
This section proposes a setup to improve (or: answer) the research-questions.
It will discuss techniques used in other projects and how implemented here.
In the subsections each used technique is further explained. (Only explained when really used)

@@

\section{Implementation}
\label{sec:Implementation}
This section will discuss implementation details.
Hardware platform (if any), software used. Complexity, precision of metrics etc.
Data-linking between algorithms, pipeline construction.

\section{Experiments, results}
\label{sec:Experiments}
This section will outline the precise experiments and gives the results of these.

\section{Discussion}
\label{sec:Discussion}
This section will discuss the results of the previous section.
It will relate the results to previous work.

\section{Conclusion}
\label{sec:Conclusion}
Conclusion (answer research question), summary of results, feature work.
